Shaping strategies and standardisation of faceted spheroids from Qianshangying (North China)

### 2025-07-03 analysis/paper/paper.qmd
updates

Raw materials at QSY were classified into four categories following [@pei2002] and [@pei2017]: lava, siliceous dolomite, chert, and others. Lava rock dominates the assemblage (n=637, 66.7%), followed by siliceous dolomite (n=209, 21.9%), with chert and other materials comprising the remainder (n=53, 5.5% and n=56, 5.9% respectively). It seems that spheroids show no strong raw material preference. Of the 12 identified spheroids, 75.0% are lava (n = 9), 16.7% are siliceous dolomite (n = 2), and 8.3% is quartzite (n=1, classified under "other"), roughly mirroring the assemblage’s overall composition except for the absence of chert. However, when compared to cores, which are 66.0% lava (n = 62), 22.3% siliceous dolomite (n = 21), 4.3% chert (n = 4), and 7.4% other (n = 7), spheroids show a higher frequency of lava use, suggesting a possible preference or selection difference in their production. (pie chart in need?)

>>>>

Raw materials at QSY were classified into four categories following [@pei2002] and [@pei2017]: lava, siliceous dolomite, chert, and others. Lava rock dominates the assemblage (n=637, 66.7%), followed by siliceous dolomite (n=209, 21.9%), with chert and other materials comprising the remainder (n=53, 5.5% and n=56, 5.9% respectively). It seems that spheroids show no strong raw material preference. Of the 12 identified spheroids, 75.0% are lava (n = 9), 16.7% are siliceous dolomite (n = 2), and 8.3% is quartzite (n=1, classified under "other"), roughly mirroring the assemblage’s overall composition except for the absence of chert. However, when compared to cores, which are 66.0% lava (n = 62), 22.3% siliceous dolomite (n = 21), 4.3% chert (n = 4), and 7.4% other (n = 7), spheroids show a higher frequency of lava use, suggesting the different preferences in raw material selection for the spheroids and the cores. (pie chart in need?)
